---
title: "allListe"
output:
  html_document:
    df_print: paged
    toc: false
---

```{r setup, include = FALSE}
begin_time <-Sys.time()
suppressWarnings(source("./R/sources.R"))
library(vtable)
```


[retour](./../index.html)  

<!-- -->
||||  
|---|---|---|  
|[allListe](./allListe.html)|[wordcloud](./wordcloud.html)|[graph](./mygraph.html)|  
|[sumup](./sumup.html)|[summary](./summary.html)|[sumUpAll](./sumUpAll.html)|


---

## HISTORIQUE ET PREMDER

### hist
```{r hist, echo=FALSE}
data <- data.frame(listDesc.desc())

data %>% select(tisaep,Horodateur...1,status...5)
```

### premder ec
```{r premDerEc, echo=FALSE}
data <- data.frame(premder.ec())

data %>% filter(tisaep.all...30 != "")  %>% select(tisaep.all...30
,date.premder.all...31) 
```

### premder
```{r premder, echo=FALSE}
data <- data.frame(premder.premder())
data
data %>% filter(tisaep.all...25 != "") %>% select(tisaep.all...25,date.premder.all...26,status.all...27) 
```

### prem der
```{r premDer, echo=FALSE}

data <- data.frame(premder.prem.der())
data %>% filter(tisaep.all...21 != "")  %>% select(tisaep.all...21
,date.premder.all...22,status.all...23) 
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## PAGE TESTS

```{r testConcl, eval=FALSE, include=FALSE}

data <- data.frame(aConcl())
data %>% filter(nc >= 1) %>% select(-date,-nc,-nbTotal,-graph,-vide,-conclucompi....)
```



<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## CATEGORIES

### debut
```{r lettre, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(episode...4 == 1,status...5=="en cours") %>% select(tisaep,Horodateur...1) 

```

### liste EC : alea
```{r alea, echo=FALSE}

data <- data.frame(listDesc.desc())
max <- 100
data %>% filter(status...5 == "en cours") %>% sample_n(max) %>% group_by(tisa) %>% summarise(pc = n()) %>% arrange(desc(pc)) %>% filter(pc >= 3)
```

### liste EC : Titre
```{r titre, echo=FALSE}
df <- data.frame(listDesc.ec())
data <- data.frame(listDesc.desc())
data <- distinct(data)
# titre = readline()
titre = df[1,2]
data %>% filter(Titre...2 == titre) %>% select(tisaep,Horodateur...1) 
if(data[2,2] == data[1,2]){
  titre = df[3,2]
} else {
  titre = df[2,2]
}
data %>% filter(Titre...2 == titre) %>% select(tisaep,Horodateur...1) 
```

### liste EC
```{r ec, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(status...5 == "en cours") %>% select(tisaep,Horodateur...1) 
```



### liste film
```{r film, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(status...5 == "film") %>% select(tisaep,Horodateur...1) 
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## NB

### nb (large)
```{r nb2, echo=FALSE}
data <- data.frame(aSmra())
        data %>% filter(titre != "") %>% mutate(sum=nbDeLignes+nbPage) %>% rename("nb"=nbDeLignes,"nbBis"=nbPage) %>% select(titre,nb,titre_1,nbBis,sum)
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## COPIE BY SCRIPT

### copy
```{r copy, echo=FALSE}
data <- data.frame(aCopyAllBis())
        data <- data[2:2]
        data %>% filter(contentAll != "")
    
```

### conclu
```{r conclu, echo=FALSE}
   data <- data.frame(aConcl())
        data <- data[2:4]
        data %>% filter(conclucompi.... != "")
    
```

### conclubis
```{r conclubis, echo=FALSE}
data <- data.frame(aConclBis())
        data <- data[2:4]
        data %>% filter(conclucompibis.... != "")
    
```

### sem
```{r sem, echo=FALSE}
data <- data.frame(copy.sem())
        data <- data[2:5]
        data %>% filter(resumesem.... != "")
```

### mois
```{r mois, echo=FALSE}
data <- data.frame(copy.mois())
        data <- data[2:5]
        data %>% filter(resumemois.... != "")
    
```

### max
```{r max, echo=FALSE}
data <- data.frame(aTestMax())
        data <- data[2:4]
        data %>% filter(max.... != "")
```

### eff
```{r eff, echo=FALSE}
data <- data.frame(aEff())
        data <- data[2:4]
        data %>% filter(eff.... != "")
```

### pageappres
```{r pageappres, echo=FALSE}
data <- data.frame(pageappres())
        data <- data[1:16]
        data %>% filter(date != "") 
```

### pageappres suppr
```{r pageappressup, echo=FALSE}
data <- data.frame(pageappressup())
        data <- data[1:16]
        data %>% filter(date != "") 
```


```{r maxall, eval=FALSE,echo=FALSE}
### max all
data <- data.frame(z00(6))
data %>% filter(X. != "") 
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>


## timing 
```{r timing , echo=FALSE}
end_time<-Sys.time()
total_time <- end_time - begin_time
print(total_time)
```
