---
title: "allListe"
output:
  html_document:
    df_print: paged
    toc: false
---

```{r setup, include = FALSE}
begin_time <-Sys.time()
suppressWarnings(source("./R/sources.R"))

```


[retour](./../index.html)  

<!-- -->
||||  
|---|---|---|  
|[allListe](./allListe.html)|[wordcloud](./wordcloud.html)|[graph](./mygraph.html)|  
|[sumup](./sumup.html)|[summary](./summary.html)|[sumUpAll](./sumUpAll.html)|


---


```{r stats3, eval=FALSE, include=FALSE}
# SUMMARY

# stats

#by(data, data$category, summary)
#Hmisc::describe(data)
#a2 <- (st(data))
#a2
accue <- data.frame(accueil())
moy <- mean(accue[3])
print(moy)
moy <- mean(accue[4])
print(moy)
#---
```

## HISTORIQUE ET PREMDER

### hist
```{r hist, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% select(tisaep,Horodateur,status)
```

### premder ec
```{r premDerEc, echo=FALSE}
data <- data.frame(premder.ec())
data %>% filter(tisaep.all_2 != "")  %>% select(tisaep.all_2
,date.premder.all_2) 
```

### premder
```{r premder, echo=FALSE}
data <- data.frame(premder.premder())
data %>% filter(tisaep.all_1 != "") %>% select(tisaep.all_1,date.premder.all_1,status.all_1) 
```

### prem der
```{r premDer, echo=FALSE}
data <- data.frame(premder.prem.der())
data %>% filter(tisaep.all != "")  %>% select(tisaep.all
,date.premder.all,status.all) 
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## CATEGORIES

### debut
```{r lettre, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(episode == 1,status=="en cours") %>% select(tisaep,Horodateur,descr.img) 

```

### liste EC : alea
```{r alea, echo=FALSE}

data <- data.frame(listDesc.desc())
max <- 100
data %>% filter(status == "en cours") %>% sample_n(max) %>% group_by(tisa) %>% summarise(pc = n()) %>% arrange(desc(pc)) %>% filter(pc >= 3)
```

### liste EC : Titre
```{r titre, echo=FALSE}
df <- data.frame(listDesc.ec())
data <- data.frame(listDesc.desc())
data <- distinct(data)
# titre = readline()
titre = df[1,2]
data %>% filter(Titre == titre) %>% select(tisaep,Horodateur) 
if(data[2,2] == data[1,2]){
  titre = df[3,2]
} else {
  titre = df[2,2]
}
data %>% filter(Titre == titre) %>% select(tisaep,Horodateur) 
```

### liste EC
```{r ec, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(status == "en cours") %>% select(tisaep,Horodateur) 
```

### liste TER
```{r ter, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(status == "terminée") %>% select(tisaep,Horodateur) 
```

### liste film
```{r film, echo=FALSE}
data <- data.frame(listDesc.desc())
data %>% filter(status == "film") %>% select(tisaep,Horodateur) 
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## NB

### nb
```{r nb, echo=FALSE}
data <- data.frame(aListes())

# df <- data.frame(cbind(data$titre,data$nbDeLignes,data$titre_1,data$nbPage))
# df[1:50,]

data %>% filter(titre != "")  %>% select(titre,nbDeLignes) 
data %>% filter(titre_1 != "")  %>% select(titre_1,nbPage) 
```

### nb (large)
```{r nb2, echo=FALSE}
data <- data.frame(aListes())
        data %>% filter(titre_1 != "") %>% mutate(sum=nbDeLignes+nbPage) %>% rename("nb"=nbDeLignes,"nbBis"=nbPage) %>% select(titre,nb,titre_1,nbBis,sum)
```

---

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## COPIE BY SCRIPT

### copy
```{r copy, echo=FALSE}
data <- data.frame(aCopyAll())
        data <- data[2:2]
        data %>% filter(tout != "")
    
```

### conclu
```{r conclu, echo=FALSE}
   data <- data.frame(aTestConclu())
        data <- data[2:4]
        data %>% filter(conclucompi.... != "")
    
```

### conclubis
```{r conclubis, echo=FALSE}
data <- data.frame(aTestConcluBis())
        data <- data[2:4]
        data %>% filter(conclucompibis.... != "")
    
```

### sem
```{r sem, echo=FALSE}
data <- data.frame(copy.sem())
        data <- data[2:5]
        data %>% filter(resumesem.... != "")
```

### mois
```{r mois, echo=FALSE}
data <- data.frame(copy.mois())
        data <- data[2:5]
        data %>% filter(resumemois.... != "")
    
```

### max
```{r max, echo=FALSE}
data <- data.frame(aTestMax())
        data <- data[2:4]
        data %>% filter(max.... != "")
```

### eff
```{r eff, echo=FALSE}
data <- data.frame(aEff())
        data <- data[2:4]
        data %>% filter(eff.... != "")
```

### pageappres
```{r pageappres, echo=FALSE}
data <- data.frame(pageappres())
        data <- data[1:16]
        data %>% filter(date != "") 
```

### pageappres suppr
```{r pageappressup, echo=FALSE}
data <- data.frame(pageappressup())
        data <- data[1:16]
        data %>% filter(date != "") 
```


```{r maxall, eval=FALSE,echo=FALSE}
### max all
data <- data.frame(z00(6))
data %>% filter(X. != "") 
```

---

## timing 
```{r timing , echo=FALSE}
end_time<-Sys.time()
total_time <- end_time - begin_time
print(total_time)
```
